---
title: "formative_test"
author: "ting"
date: "October 5, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

5. DI stands for De-identified. That means personal information is removed usually for privacy protection.
```{r}
D1= read.csv("~/Downloads/dataverse_files/HMXPC13_DI_v2_5-14-14.csv", head=TRUE)

n_CS50x_2012 = nrow(subset(D1, certified == 1 & course_id=="HarvardX/CS50x/2012"))
```

6. n_CS50x_2012 = 1287

```{r}

n_CS50x_2012_otc.15_Colombia = nrow(subset(D1, registered == 1 & course_id=="HarvardX/CS50x/2012" & start_time_DI == "2012-10-15" & final_cc_cname_DI =="Colombia"))



```
7. 10 people registered for HarvardX/CS50x from Columbia on October 15, 2012.


```{r}
D2_AAA= subset (D1, final_cc_cname_DI == "United States")
D2= subset (D2_AAA, select = c(userid_DI, start_time_DI, final_cc_cname_DI))

```


8. D2

9. 
```{R}
library(tidyr)
D3 = subset(D1, select = c(registered, userid_DI, start_time_DI))
D3 = unique(D3)
D3_BBB= spread(D3, start_time_DI, registered)

```

10. Now make the row names of D3 the student ids on your new data frame and remove the user id column from your data frame

```{r}
D4 = D3_BBB
row.names(D4)=D3_BBB$userid_DI
D4 = subset(D4, select = -c(userid_DI))
#D3_BBB = subset(D3_BBB, select = -c(userid_DI))

```

11. 
```{R}
M1 = data.matrix(D3_BBB)
```

12.
```{r}
M2 = t(M1)
```

13. 
```{r}
#M3 = M1%*%M2
```
If two students register at the same date, M1 x M2 should give 1, therefore, we can calculate M3 = M1%*%M2.
However, my laptop cannot handle the computation. So I do not run it.

14. 

```{r}
#diag(M3) =  NA
```

